Separating Use and Reuse to Improve Both

### 2017-05-18 FACS/paper.tex
Abstract

\begin{abstract}
In most object oriented languages subclassing/code-reuse implies
subtyping. This is considered by many a conceptual design error, but it
seems required by technical reasons.

This paper synthesizes an OO language design for a nominally typed
language that allows code-reuse and subtyping to be decoupled using a
form of \emph{traits}. This design improves on previous work by
Damiani and Servetto by proving a simpler and more natural model for
OO programmers. We provide a novel and elegant solution to uniformly
handle behavior and state within trait composition.  By making our
type system distinguish between code use and code reuse we can avoid
many redundant abstract declarations that were required in previous
work by Servetto and Damiani, while supporting self construction,
binary methods and recursive types.

>>>>

\begin{abstract}
In most object oriented languages subclassing/code-reuse implies
subtyping. This is considered by many a conceptual design error, but it
seems required for technical reasons.

This paper synthesizes an OO language design for a nominally typed
language that allows code-reuse and subtyping to be decoupled using a
form of \emph{traits}. This design improves on previous work by
Damiani and Servetto by proving a simpler and more natural model for
OO programmers. By making our
type system distinguish between code use and code reuse we can avoid
many redundant abstract declarations that were required in previous
work by Servetto and Damiani, while supporting self construction,
binary methods and recursive types. Moreover, we provide a novel and elegant solution to uniformly
handle behavior and state within trait composition.
